% resume.tex
% vim:set ft=tex spell:

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{chemformula}
\usepackage{tgpagella}
\usepackage{verbatim}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

%%%
%%% contact info and headings
%%%
\begin{center}
{\LARGE \textbf{Kraig J. Andrews}}

61943 Mustang Drive\ \ \textbullet South Lyon, MI 48178
\\
+1 (248) 798-9388\ \ \textbullet
\ \ kraigandrews1992@gmail.com
\end{center}

%%%
%%% relevant education
%%%
\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
	\parskip=0.1em

    % Phd
    \item 
    \headerrow
        {\textbf{Wayne State University}}
        {\textbf{Detroit, MI}}
    \\
    \headerrow
        {\emph{Ph.D. Physics}}
        {\emph{2014 -- Present}}
        \begin{itemize*}
        	\item[]
        	\emph{Thesis Title:} ``Quantum Transport Properties and Scattering Mecahnisms in Transistion \\
        	Metal Dichalcogenides''
        \end{itemize*}
%    \begin{itemize*}
        %\item\emph{Advisor:} Dr. Zhixian Zhou
        %\item\emph{Thesis Title:} ``Quantum Transport Properties and Scattering Mechanisms in Transition Metal Dichalcogenides'' 
%    \end{itemize*}
    
    % Masters
    \item 
    \headerrow
        {\textbf{Wayne State University}}
        {\textbf{Detroit, MI}}
    \\
    \headerrow
	{\emph{M.Sc. Physics}}
        {\emph{2014 -- 2017}}

    % B.S. number 1
	\item 
	\headerrow
	{\textbf{Michigan State University}}
	{\textbf{East Lansing, MI}}
	\\
	\headerrow
	{\emph{B.Sc. Physics}}
        {\emph{2010 -- 2014}}
    
    % B.S. number 2
    \item 
    \headerrow
        {\textbf{Michigan State University}}
        {\textbf{East Lansing, MI}}
    \\
    \headerrow
        {\emph{B.Sc. Astrophysics}}
        {\emph{2010 -- 2014}}

\end{itemize}

%%%
%%% relevant experience
%%%
\hrule
\vspace{-0.4em}
\subsection*{Research Experience}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{Nano Fabrication and Electron Transport Laboratory}}
		{\textbf{Wayne State University, Detroit, MI}}
	\\
	\headerrow
		{\emph{Graduate Research Assistant (Advisor: Dr. Zhixian Zhou)}}
		{\emph{2015 -- Present}}
	\begin{itemize*}
		\item Fabricate field-effect transistors using two-dimensional semiconductors to invesitgate their intrinsic transport properties. 
		\item Develop novel techniques for making low-resistance Ohmic contacts to a wide variety of 
		two-dimensional semiconductors.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{National Institute of Materials Science (NIMS)}}
		{\textbf{Tsukuba, Ibaraki Prefecture, Japan}}
	\headerrow
		{\textbf{International Center for Materials Nanoarcitectonics (MANA)}}
		{\textbf{}}
	%\\
	\headerrow
		{\emph{Visiting Graduate Researcher (Advisor: Dr. Kazuhito Tsukagoshi)}}
		{\emph{2017}}
	\begin{itemize*}
		\item Investigate methods for surface modification of two-dimensional semiconductors for
		the use of creating a new low-resistance Ohmic contact strategy.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{Interational Course on Computational Physics}}
		{\textbf{Delft, The Netherlands and East Lansing, MI}}
	\\
	\headerrow
		{\emph{Undergraduate Research Assistant (Advisors: Dr. Jos Thijssen, Dr. Phil Duxbury)}}
		{\emph{2014}}

	\begin{itemize*}
		\item A Joint collaboration with Technische Universiteit Delft and Michigan State University involving the development of 
		computational models of various physical systems to model interactions of materials and optimize employed techniques.
	\end{itemize*}

	\item 
	\headerrow
		{\textbf{Jenoptik Laser Technologies}}
		{\textbf{Brighton, MI}}
	\\
	\headerrow
		{\emph{Summer Intern}}
		{\emph{2013}}
	\begin{itemize*}
		\item Contributed in development of a user interface for laser welding machine
		that allows user manipulation of robotic end-arm tooling.
		\item Incorporated microcontroller program via interfaced electronic devices and 
		several developed algorithms to analyze physical data and feedback in real-time. 
	\end{itemize*}

	\item 
	\headerrow
		{\textbf{Michigan State University}}
		{\textbf{East Lansing, MI}}
	\\
	\headerrow
		{\emph{Undergraduate Research Assistant  (Advisor: Dr. Edward Brown)}}
		{\emph{2012 -- 2014}}
	\begin{itemize*}
		\item Research of neutron star evolution using various modeling tools and techniques. 
	\end{itemize*}
\end{itemize}

%%%
%%% relevant talks
%%%
\hrule
\vspace{-0.4em}
\subsection*{Peer Review Publications}

\begin{enumerate*}
	\parskip=0.1em
	\item ``\emph{High Performance \ch{WSe2} Phototransistors with 2D/2D Ohmic Contacts.}''
		Tianjiao Wang, \textbf{Kraig Andrews}, Arthur Bowman, Tu Hong, Michael Koehler, Jiaqiang Yan, David Mandrus, Zhixian Zhou, and Ya-Qiong Xu. \emph{Nano Letters, (18)}5:2766-2771. 2018.
%	\item ``\emph{}''
%	\item ``\emph{}''
\end{enumerate*}

%%%
%%% relevant talks
%%%
\hrule
\vspace{-0.4em}
\subsection*{Presentations}

\begin{enumerate*}
	\parskip=0.1em
	\item ``\emph{Palladium Diselenide as a New Two-Dimensional Electronic Material Beyond Silicon.}'' 
	\textbf{Kraig Andrews}, Arthur Bowman, Upendra Rijal, Amanda Haglund, David Mandrus, and Zhixian Zhou.
	Society of Vacuum Coaters TechCon, Orlando, FL. May 2018.

	\bigskip

	\item ``\emph{Improved On-Off in Ratio Black Phosphorus Field-Effect Transistors with True Ohmic Contacts.}''  
	\textbf{Kraig Andrews}, Arthur Bowman, Upendra Rijal, Michael Koehler, David Mandrus, and Zhixian Zhou. 
	APS March Meeting, Los Angeles, CA. March 2018.

	\bigskip

	\item ``\emph{High Mobility Palladium Diselenide Field-Effect Transistors Using Heaving $n-$Doped Graphene Contacts.}''
	Arthur Bowman, \textbf{Kraig Andrews}, Upendra Rijal, Amanda Haglund, David Mandrus, and Zhixian Zhou.
	APS March Meeting, Los Angeles, CA. March 2018.

	\bigskip

	\item ``\emph{Measuring the Barrier Height at Transition Metal Dichalcogenide Heterojunctions.}''
	Upendra Rijal, Arthur Bowman, \textbf{Kraig Andrews}, Michael Koehler, David Mandrus, and Zhixian Zhou.
	APS March Meeting, Los Angeles, CA. March 2018.

	\bigskip

	\item ``\emph{High-Performance Top-Gated \ch{WSe2} Transistors with Two-Dimensional Ohmic Contacts.}''
	\textbf{Kraig Andrews}, Upendra Rijal, Arthur Bowman, Hsun-Jen Chuang, Sagar Paduel, Michael Koehler, David Mandrus, and Zhixian Zhou.
	41$^\mathrm{st}$ Annual Symposium American Vacuum Society- Michigan Chapter, Ann Arbor, MI. May 2017.

	\bigskip

	\item ``\emph{Substrate Dependence of Hall and Field-Effect Mobilities in Few-Layer \ch{MoS2} Field-Effect Transistors.}''
	Bhim Chamlagain, Perera Meeghage, Hsun-Jen Chuang, Arthur Bowman, Upendra Rijal, \textbf{Kraig Andrews}, Joseph Klesko,
	Charles Winter, and Zhixian Zhou. APS March Meeting, Boston, MA, March 2016.
\end{enumerate*}

%%% 
%%% awards and honors
%%%
\hrule
\vspace{-0.4em}
\subsection*{Awards and Honors}
	
	\begin{itemize*}
		\parskip=0.1em
		\item[]
			\headerrow
			{Frank Knoller Endowed Fellowship in Physics}
			{2019}

		\item[]
			\headerrow
			{Society of Vacuum Coaters (SVC) Student Sponsorship Award}
			{2018}

		\item[]
			\headerrow
			{Wayne State Physics and Astronomy Department Travel Award}
			{2017}

		\item[]
			\headerrow
			{Associated Students of Michigan State University (ASMSU) Research Travel Grant}
			{2014}
	\end{itemize*}

%%%
%%% professional membership
%%%
\hrule
\vspace{-0.4em}
\subsection*{Professional Memberships}

	\begin{itemize*}
		\parskip=0.1em
		\item[]
		\headerrow
			{Society of Vacuum Coaters}
			{2018}

		\item[]
		\headerrow
			{American Physical Society}
			{2017 -- Present}

		\item[]
		\headerrow
			{Sigma Pi Sigma, Physics Honor Society}
			{2013}

	\end{itemize*}

%%% 
%%% volunteer experience
%%%
\hrule
\vspace{-0.4em}
\subsection*{Volunteer and Outreach Experience}

	\begin{itemize*}
		\parskip=0.1em
		\item[]

	\end{itemize*}

%%%
%%% courses taught
%%%
\hrule
\vspace{-0.4em}
\subsection*{Teaching Experience}

\begin{itemize*}
	\parskip=0.1em
	%\begin{comment}
	\item[]
	\headerrow
		{Laboratory Instructor, General Physics I, Wayne State University}
		{Summer 2018}

	\item[]
	\headerrow
		{Teaching Assistant, General Physics II, Wayne State University}
		{Summer 2018}

	\item[]
	\headerrow
		{Teaching Assistant, General Physics I, Wayne State University}
		{Winter 2018}

	\item[]
	\headerrow
		{Teaching Assistant, General Physics II, Wayne State University}
		{Autumn 2017}

	\item[]
	\headerrow
		{Teaching Assistant, General Physics II, Wayne State University}
		{Winter 2017}

	\item[]
	\headerrow
		{Teaching Assistant, General Physics II, Wayne State University}
		{Autumn 2016}

	\item[]
	\headerrow
		{Teaching Assistant, General Physics I, Wayne State University}
		{Summer 2016}

	\item[]
	\headerrow
		{Teaching Assistant, General Physics I, Wayne State University}
		{Autumn 2015}
	
	\item[]
	\headerrow
		{Teaching Assistant, General Physics Lab I, Wayne State University}
		{Summer 2015}

	\item[]
	\headerrow
		{Laboratory Instructor, Conceptual Physics Lab I, Wayne State University}
		{Winter 2015}

	\item[]
	\headerrow
		{Laboratory Instructor, Descriptive Astronomy Lab I, Wayne State University}
		{Autumn 2014}

	\item[]
	\headerrow
		{Teaching Assistant, Introductory Physics II, Michigan State University}
		{Winter 2014}

	\item[]
	\headerrow
		{Laboratory Instructor, Planets and Telescopes, Michigan State University}
		{Winter 2013}

	\item[]
	\headerrow
		{Teaching Assistant, Introductory Physics I, Michigan State University}
		{Autumn 2013}

	\item[]
	\headerrow
		{Teaching Assistant, Introductory Physics II, Michigan State University}
		{Winter 2012}
	%\end{comment}

	\begin{comment}
	\item[]
	\headerrow
		{Teaching Assistant, Wayne State University}
		{Autumn 2014 -- Summer 2018}
	\item[]
	\headerrow
		{Teaching Assistant, Michigan State University}
		{Winter 2012 -- Winter 2014}
	\end{comment}

\end{itemize*}

%%%
%%% relevant skills
%%%
\hrule
\vspace{-0.4em}
\subsection*{Core Technical Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[Nanofabrication:]
	Atomic force microscopy (AFM), Electron beam lithography, Photolithography, Scanning electron microscopy (SEM), General clean room abilities (> 1000 hours), Physical vapor deposition (PVD), Plasma etching, Reactive ion etching (RIE)
	\item[Languages \& Software:]
	\CPP, Fortran, Java, JavaScript, \LaTeX, Python, shell script, Microsoft Office, Matlab, Mathematica
	\item[Operating Systems:]
	OS X, Linux OS, Microsoft Windows
\end{description*}
\end{indentsection}

\end{document}
